\bf\mftitle

### 2011-02-28 doc/jInfer/projecttype/projecttype.tex
#3187361 projecttype doc

\code{JInferProjectFactory} is a factory class implementing \code{ProjectFactory} interface provided by NBP. This class is responsible for loading/saving of jInfer project from/to file-system and also determining if folder in file-system is type of jInfer project (contains \emph{jinferproject} sub-folder). For this purpose, class has three methods: \code{isProject()}, \code{save()} and \code{load()}. When jInfer project is loaded from file-system, \code{JInferProjectFactory} creates new instance of \code{JInferProject} passing path to project folder as a constructor parameter. When \code{save()} method is invoked, all the project properties are saved in \emph{projectproperties} file and paths to input files are saved in \emph{input.files}.

@@

\code{InputFiles} is utility class that stores/loads input file paths into/from input.files XML file. For this purpose, class uses \emph{JAXB} \cite{JAXB} architecture to unmarshall/marshall XML file into/from java content objects. XML structure of the input.files is very simple, \emph{jinferinput} is root element under which are \emph{documents}, \emph{schemas} and \emph{queries} elements. Each of this elements could have none or more \emph{file} elements with string attribute \emph{loc} that contains absolute path to input file.\\

@@

Each of the \emph{input} nodes is represented by \code{FolderNode} class and contains \emph{input file} nodes (represented by \code{FileNode} class) representing files added to the jInfer project. Notice that these \emph{input file} nodes represents files from file-system and are not copied to project folder structure. Because of this, if you delete this nodes from project tree, files from file-system are not deleted.\\

@@

First of the two actions, after it was invoked, file choose dialog is opened which has set file filter according to available classes that implement \code{Processor} interface registered in jInfer with \code{ServiceProvider}. After selecting files in dialog, these files are inserted into particular \emph{input file} node according to mapping of file extension to folder type gained from \code{Processor} classes. If no mapping for some extension exists, this file is inserted into folder which is defined in \emph{Miscellaneous} properties category (section \ref{pref}).\\

Run action, which is available in root node context menu, is also present in NBP toolbar as a \emph{Run} button and in jInfer Welcome window. This action is implemented in \code{RunAction} class and simply invokes \jmodule{Runner}s \code{run()} method, if no other inference is already running, otherwise information dialog pops up informing about already running inference. This check is done with \code{setActiveProject()} from \code{RunningProject} class (section \ref{running-project}).

@@

To this group of actions belong two actions: action for adding input files into \emph{input folder} node (\code{FileAddAction} class) and action for deleting all input files in \emph{input folder} node (\code{DeleteAllAction} class). \code{FileAddAction} class implements action which opens file choose dialog and selected files are added into particular \emph{file input}node. \code{DeleteAllAction} class simply removes all input files previously added into particular \emph{file input} node.

@@

TODO what kind of validation did we use. How to extend validation.\\

\code{ValidateAction} class implements action, which allows documents and schema files to be validated against each other. Because of this, action is presented in context menu of document and schema files (in actual implementation is available for XML, dtd and XML schema files). Unlike the other action classes, this extends NBP \code{NodeAction} class, which allows to enable/disable action in context menu according to node selection. Action is enabled only if exactly one schema file is selected and one or more XML files. If the selected XML files are valid against selected schema, information dialog is popped up, otherwise error dialog is popped up and in \emph{validate} output window is printed error message describing cause of non-validity XML files against schema.

@@

Category in a properties window is represented by NB platform \code{ProjectCustomizer.Category} class and properties pane is represented by \code{JPanel} class. Classes responsible for creation of this properties window are\\ \code{JInferCustomizerProvider} and \code{JInferComponentProvider}. From Jinfer module point of view is properties category represented by \code{PropertiesPanelProvider} interface and associated properties pane by \code{AbstractPropertiesPanel} abstract class. How to use this interface and abstract class to create custom project properties category presented in jInfer project type properties windowis described in section \ref{properties_reg}.\\

@@

\noindent\code{PropertiesPanelProvider} interface provides the following methods:
\begin{itemize}
	\item getName() - Gets a programmatic name of category
	\item getDisplayName() - Gets a name of category displayed in properties window.
	\item getPriority() - Gets a priority of category, by which is sorted among other sibling categories in a tree.
	\item getPanel(Properties) - Gets \code{AbstractPropertiesPanel} representing the category properties pane. The only parameter is instance of \code{Properties} class to which are saved properties which were set in \emph{properties pane}.
	\item getParent() - getter for a programmatic name of category which is parent of this category in a tree hierarchy.
	\item getSubCategories() - Gets a \code{List} of \code{VirtualCategoryPanel} representing virtual category child.
\end{itemize}

@@

\noindent\code{VirtualCategoryPanel} extends \code{JPanel} and its constructor has three parameters:
 \begin{itemize}
	\item \code{categoryId} - programmatic name of the category or ID.
	\item \code{categoryName} - human readable name of the category displayed in jInfer properties window.
	\item \code{modules} - \code{List<? extends NamedModule>} of modules that will be children of this virtual category.
\end{itemize}

@@

\begin{verbatim}
public class ProjectPropertiesPanel extends AbstractPropertiesPanel {

@@

  public ProjectPropertiesPanel(final Properties properties) {
    super(properties);
    init();
  }

@@

This section describes ability of jInfer to create new jInfer project through \emph{new project} wizard. This wizard contains two steps, where first is standard one with project name and location selection, and the second is the selection of Initial grammar module, Simplifier and Schema generator module which will be used in inference for newly created module. In the new project creation process can be already finished in a first step, in that case, default modules will be used for inference. After finishing of the wizard, new jInfer project type is created with typed name in selected location. It is important to notice that package \code{cz.cuni.mff.ksi.jinfer.projecttype} contains \code{JInferTemplateProject.zip} file, in which is default folder structure of the jInfer project type, and the content of a zip is copied into location defined in the wizard. For more information, how to create new project wizard,  please look at \cite{project_sample}.\\

@@

Also jInfer project type has its own properties category in a project properties window and is called \emph{Miscellaneous}. In this category,
two properties can be set. First property is default \emph{input file} folder to which is inserted input file selected from \emph{FilesAddAction}, that has extension, which is not defined by any \code{Processor} registered in jInfer. Second property is global \emph{LOG} level, which defines the minimum level of messages that will be displayed in jInfer output window. If some module has its own \emph{LOG} level setting, global settings are overridden by these.

>>>>

\code{JInferProjectFactory} is a factory class implementing \code{ProjectFactory} interface provided by NBP. This class is responsible for loading/saving of jInfer project from/to file-system and also determining if folder in file-system is type of jInfer project (contains \emph{jinferproject} sub-folder). For this purpose, class has three methods: \code{isProject()}, \code{save()} and \code{load()}. When jInfer project is loaded from file-system, \code{JInferProjectFactory} creates new instance of \code{JInferProject} passing path to project folder as a constructor parameter. When \code{save()} method is invoked, all the project properties are saved in \emph{project.properties} file and paths to input files are saved into \emph{input.files}.

@@

\code{InputFiles} is utility class that stores/loads input file paths into/from \emph{input.files} XML file. For this purpose, class uses \emph{JAXB} \cite{JAXB} architecture to unmarshall/marshall XML file into/from java content objects. XML structure of the input.files is very simple, \emph{jinferinput} is root element under which are \emph{documents}, \emph{schemas} and \emph{queries} elements. Each of this elements could have none or more \emph{file} elements with string attribute \emph{loc} that contains absolute path to input file.\\

@@

Each of the \emph{input} nodes is represented by \code{FolderNode} class and contains \emph{input file} nodes (represented by \code{FileNode} class) representing files added to the jInfer project. Notice that these \emph{input file} nodes represents files from file-system and are not copied to the project folder structure. Because of this, if you delete this nodes from project tree, files from file-system are not deleted.\\

@@

First of the two actions, after its invocation, file choose dialog is opened which has set file filter according to available classes that implement \code{Processor} interface registered in jInfer with \code{ServiceProvider}. After selecting files in dialog, these files are inserted into particular \emph{input folder} node according to mapping of file extension to folder type gained from \code{Processor} classes. If no mapping for some extension exists, this file is inserted into folder which is defined in \emph{Miscellaneous} properties category (section \ref{pref}).\\

Run action, which is available in root node context menu, is also present in NBP toolbar as a \emph{Run} button and in jInfer Welcome window. This action is implemented in \code{RunAction} class and simply invokes \jmodule{Runner}s \code{run()} method, if no other inference is already running, otherwise information dialog pops up, informing about already running inference. This check is done with \code{setActiveProject()} from \code{RunningProject} class (section \ref{running-project}).

@@

To this group of actions belong two actions: action for adding input files into \emph{input folder} node (\code{FileAddAction} class) and action for deleting all input files in \emph{input folder} node (\code{DeleteAllAction} class). \code{FileAddAction} class implements action which opens file choose dialog and selected files are added into particular \emph{input folder} node. \code{DeleteAllAction} class simply removes all input files previously added into particular \emph{input folder} node.

@@

\code{ValidateAction} class implements action, which allows documents and schema files to be validated against each other. Because of this, action is presented in context menu of document and schema files (in actual implementation is available for XML, dtd and XML schema files). Unlike the other action classes, this extends NBP \code{NodeAction} class, which allows to enable/disable action in context menu according to node selection. Action is enabled only if exactly one schema file is selected and one or more XML files. If the selected XML files are valid against selected schema, information dialog is popped up, otherwise error dialog is popped up and in \emph{validate} output window is printed error message describing cause of non-validity XML files against schema.\\

For the validation against XML Schema, we use standard Java validation API \cite{xml_validate}. Besides XML Schema, this API allows to  validate XML also against \emph{Relax NG} and \emph{Schematron} schema. If you want to extend the functionality of one of these schemas, you need to set \code{schemaLanguage} local variable to appropriate \code{XMLConstant}. If you need to extend validation to some other type of schema, you can use dtd validation as a sample.\\

For a validation error handling is used \code{JInferErrorHander} class which extends \code{DefaultHandler} class and overrides \code{error()} and \code{fatalError()} methods from this class. In these methods is created error message, which is consequently printed in validation \emph{output} window.

@@

Category in a properties window is represented by NB platform \code{ProjectCustomizer.Category} class and properties pane is represented by \code{JPanel} class. Classes responsible for creation of this properties window are\\ \code{JInferCustomizerProvider} and \code{JInferComponentProvider}. From Jinfer module point of view is properties category represented by \code{PropertiesPanelProvider} interface and associated properties pane by \code{AbstractPropertiesPanel} abstract class. How to use this interface and abstract class to create custom project properties category presented in jInfer project type properties window is described in section \ref{properties_reg}.\\

@@

\noindent\code{PropertiesPanelProvider} interface provides the following methods:
\begin{itemize}
	\item getName() - Gets a programmatic name of category.
	\item getDisplayName() - Gets a name of category displayed in properties window.
	\item getPriority() - Gets a priority of category, by which is sorted among other sibling categories in a tree.
	\item getPanel(Properties) - Gets the \code{AbstractPropertiesPanel} instance representing the category \emph{properties pane}. The only parameter is instance of \code{Properties} class to which are saved properties which were set in \emph{properties pane}.
	\item getParent() - Getter for a programmatic name of category which is parent of this category in a tree hierarchy.
	\item getSubCategories() - Gets a \code{List} of \code{VirtualCategoryPanel} instances representing virtual category children.
\end{itemize}

@@

\noindent\code{VirtualCategoryPanel} extends \code{JPanel} and its constructor has three parameters:
 \begin{itemize}
	\item \code{categoryId} - programmatic name of the category or ID.
	\item \code{categoryName} - human readable name of the category displayed in jInfer properties window.
	\item \code{modules} - \code{List<?\ extends NamedModule>} of modules that will be children of this virtual category.
\end{itemize}

@@

\begin{verbatim}
public class ExamplePropertiesPanel extends AbstractPropertiesPanel {

@@

  public ExamplePropertiesPanel(final Properties properties) {
    super(properties);
    init();
  }

@@

This section describes ability of jInfer to create new jInfer project through \emph{new project} wizard. This wizard contains two steps, where first is standard one with project name and location selection, and the second is the selection of Initial grammar module, Simplifier and Schema generator module which will be used in inference for newly created module. New project creation process can be already finished in a first step, in that case, default modules will be used for inference. After finishing of the wizard, new jInfer project type is created with typed name in selected location. It is important to notice that package \code{cz.cuni.mff.ksi.jinfer.projecttype} contains \code{JInferTemplateProject.zip} file, in which is default folder structure of the jInfer project type, and the content of a zip is copied into location defined in the wizard. For more information, how to create new project wizard,  please look at \cite{project_sample}.\\

@@

Also jInfer project type has its own properties category in a project properties window called \emph{Miscellaneous}, and it is implemented by \code{ProjectPropertiesPanelProvider} and \code{ProjectPropertiesPanel} classes. In this category, two properties can be set. First property is default \emph{input file} folder to which is inserted input file selected from \emph{FilesAddAction}, that has extension which is not defined by any \code{Processor} registered in jInfer. Second property is global \emph{LOG} level, which defines the minimum level of messages that will be displayed in jInfer output window. If some module has its own \emph{LOG} level setting, global settings are overridden by these.
